---
title: "Penguins ANOVA"
author: "Ashley Stroud"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load packages and read in the penguins.csv data


```{r}

library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")

#if you want git to have record of intermediate, you need to commit and push it before saving

```

Our question:

Is there a sig difference in mean flipper length for female penguins by species (Chinstrap, Gentoo, and Adelie)?

2. Do some exploring (data already in tidy, each column is a variable, each row is a observation)

New functions: with  + table function for easy counting over multiple factors. 

Update species name with case_when

```{r}

#first, i want to know how many counts i have by male and female. look up with, ?with

counts <- with(penguins, table(species, sex))

penguins2 <- penguins %>% 
  mutate(common_name=
           case_when(
             species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap",
             species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo",
             species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
           )
         ) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")


```


- Exploratory graphs
- Summary statistics
- Levene's test for equal variance
- one-way ANOVA
- post-hoc testing




